### 2016-08-12 docs/ms_communitySynchrony.tex
changing to bw figs

\documentclass[12pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={},
            colorlinks=true,
            citecolor=blue,
            urlcolor=black,
            linkcolor=black,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{0}

@@

\textbf{Keywords}: synchrony, compensatory dynamics, environmental stochasticity, demographic stochasticity, interspecific competition, stability

\textbf{Authorship}: ATT, CdM, and PBA designed the research. CdM and ML designed and analyzed the theoretical model. ATT and PBA performed the empirical analysis. All authors contributed to the interpretation and presentation of results. ATT wrote the first draft of the manuscript, and all authors contributed to manuscript revisions.

\textbf{Running Title}: Drivers of species synchrony in natural plant communities

\textbf{Article Type}: Letter

\textbf{Number of Words}: Abstract = 136; Main Text = 4992

\textbf{Number of References}: 46

\textbf{Number of Tables and Figures}:  2 Tables;  3 Figures

@@

\begin{abstract}
Temporal asynchrony among species \textcolor{blue}{helps} diversity \textcolor{blue}{to} stabilize ecosystem functioning, but identifying the mechanisms that determine synchrony remains a challenge.
Here, we refine and test theory showing that synchrony depends on three factors: species responses to environmental variation, interspecific \textcolor{blue}{interactions}, and demographic stochasticity. We then conduct simulation experiments with empirical population models to quantify the relative importance of these factors in five plant communities.
\textcolor{blue}{We found} that the average synchrony of per capita growth rates, which can range from 0 (perfect asynchrony) to 1 (perfect synchrony), was higher when environmental variation was present (0.62) rather than absent (0.43).
Removing interspecific \textcolor{blue}{interactions} and demographic stochasticity had small effects on synchrony. In these plant communities, where species interactions and demographic stochasticity have little influence, synchrony reflects the covariance in species responses to the environment.
\end{abstract}

\newpage{} \setlength{\parindent}{5ex}

@@

Ecosystems are being transformed by species extinctions (Cardinale et
al. 2012), changes in community composition (Vellend et al. 2013,
Dornelas et al. 2014), and anthropogenic environmental change (Vitousek
et al. 1997), impacting the provisioning and stability of ecosystem
services (Loreau et al. 2001, Hooper et al. 2005, Rockstrom et al.
2009). Experiments have provided compelling evidence that decreases in
species richness will decrease productivity (Tilman et al. 2001) and the
temporal stability of productivity (Tilman et al. 2006, Hector et al.
2010). The stabilizing effect of species richness stems from individual
species responding \textcolor{blue}{in different ways} to environmental
fluctuations (environmental stochasticity), or fluctuating
asynchronously because of random chance events (demographic
stochasticity) (Isbell et al. 2009, Hector et al. 2010, {{de
Mazancourt}} et al. 2013). Species richness affects synchrony because
larger species pools are more likely to contain species that respond
disimilarly to environmental conditions (Yachi and Loreau 1999),
implying that species losses will reduce ecosystem stability. Even
without species losses, abiotic homogenization can weaken compensatory
dynamics and, in turn, decrease temporal stability of ecosystem
functioning (Hautier et al. 2014).
\textcolor{blue}{The link between synchrony and stability means that a mechanistic understanding of synchrony can help us predict the impacts of global change on ecosystem stability.}

Theory identifies three main determinants of species synchrony:
environmental stochasticity, demographic stochasticity, and
\textcolor{blue}{interspecific interactions} (Loreau and {{de
Mazancourt}} 2008, 2013, Gonzalez and Loreau 2009). For example, in a
community composed of large \textcolor{blue}{populations} (no
demographic stochasticity)
\textcolor{blue}{with weak interspecific interations}, community-wide
species synchrony should be determined by the covariance of species'
responses to the environment (Loreau and {{de Mazancourt}} 2008).
However, \textcolor{blue}{this} prediction relies on a relatively simple
population model and only holds under two assumptions: (i) species'
responses to the environment are similar in magnitude and (ii) all
species have similar growth rates.
\textcolor{blue}{Whether such theoretical predictions hold in natural communities where species differences are unlikely to be symmetrical is unkown because few studies have explicitly tested theory on the drivers of species synchrony in natural communities}
(Mutshinda et al. 2009, Thibaut et al. 2012),
\textcolor{blue}{and they did not consider demographic stochasiticity.}

In grasslands, most empirical studies have focused on whether species
synchrony is primarily an outcome of species-specific responses to
environmental conditions (Hautier et al. 2014) or competition (Gross et
al. 2014). Even beyond grassland studies, whether competition or
environmental responses drive compensatory dynamics remains
controversial (reviewed in Gonzalez and Loreau 2009). In part,
controversy remains because quantifying the relative strengths of each
driver on the degree of synchrony from
\textcolor{blue}{the covariance matrix of species abundances} (e.g.,
Houlahan et al. 2007) is impossible. This is because an unbiased null
expectation for synchrony does not exist (Loreau and {{de Mazancourt}}
2008) and observed synchrony can arise from non-unique combinations of
factors (Ranta et al. 2008). For example, weak synchrony of population
abundances could reflect positive environmental correlations
(synchronizing effect) offset by strong competition (desynchronizing
effect), or negative environmental correlations and weak competition.

The best way to quantify the effects of environmental stochasticity,
demographic stochasticity, and interspecific
\textcolor{blue}{interactions} is to remove them one-by-one, and in
combination. In principle, this could be done in an extremely controlled
laboratory setting, but empirically-based models of interacting
populations, fit with data sets from natural communities, offer a
practical alternative. For example, Mutshinda et al. (2009) fit a
dynamic population model to several community time series of insect and
bird abundances. They used a statistical technique to decompose temporal
variation into competition and environmental components, and found that
positively correlated environmental responses among species determined
community dynamics. Thibaut et al. (2012)
\textcolor{blue}{used a similar approach for reef fish and came to a similar conclusion: environmental responses determine synchrony.}
While a major step forward, Mutshinda et al.'s (2009) and Thibaut et
al.'s (2012) modeling technique relied on abundance data that may or may
not reliably capture competitive interactions that occur at the
individual level. Furthermore, although both studies quantified the
relative importance of environmental stochasticity and
\textcolor{blue}{interspecific interactions} to explain the observed
variation of species synchrony, they did not use the model to quantify
how much synchrony would change when each factor is removed.

Here, we use multi-species population models fit to long-term
demographic data from five semi-arid plant communities to test theory on
the drivers of species synchrony. Our objectives are to (1) derive and
test theoretical predictions of species synchrony and (2) determine the
relative influence of environmental stochasticity, demographic
stochasticity, and interspecific \textcolor{blue}{interactions} on
species synchrony in natural plant communities. To achieve these
objectives, we first refine theory that has been used to predict the
effects of species richness on ecosystem stability ({{de Mazancourt}} et
al. 2013) and species synchrony (Loreau and {{de Mazancourt}} 2008) to
generate predictions of community-wide species synchrony under two
limiting cases derived from the dynamics of individual species in
monoculture. We then confront our theoretical predictions with
simulations from the empirically-based population models. Second, we use
the multi-species population models to perform simulation experiments
that isolate the effects of environmental stochasticity, demographic
stochasticity, and interspecific \textcolor{blue}{interactions} on
community-wide species synchrony. Given that our population models
capture the essential features of community dynamics important to
synchrony (density-dependence, and demographic and environmental
stochasticity), and that these models successfully reproduce observed
community dynamics (Chu and Adler 2015), perturbing the models can
reveal the processes that determine species synchrony in our focal
grassland communities.

@@

While existing theory has identified the factors driving synchrony, we
do not have a simple expression to predict synchrony in a particular
community with all factors operating simultaneously. However, we can
derive analytical predictions for species synchrony under special
limiting cases.
\textcolor{blue}{The limiting case predictions we derive serve as baselines to help us interpret results from empirically-based simulations (described below).}
We focus on synchrony of per capita growth rates, rather than
abundances, because growth rates represent the instantaneous response of
species to the environment and competition, and are less susceptible to
the legacy effects of drift and disturbance (Loreau and {{de
Mazancourt}} 2008). We present equivalent results for synchrony of
species abundances in the Online Supporting Information, and show that
they lead to the same overall conclusions as synchrony of per capita
growth rates. Following Loreau and {{de Mazancourt}} (2008) and {{de
Mazancourt}} et al. (2013), we define population growth, ignoring
observation error, as

@@

\noindent where \(N_i(t)\) is the biomass of species \emph{i} in year
\emph{t}, and \(r_i(t)\) is its population growth rate in year \emph{t}.
\(r_{mi}\) is species \emph{i}'s intrinsic rate of increase, \(K_i\) is
its carrying capacity, and \(\alpha_{ij}\) is the interspecific
competition coefficient representing the effect of species \emph{j} on
species \emph{i}. Environmental stochasticity is incorporated as
\(\sigma_{ei}u_{ei}(t)\), where \(\sigma_{ei}^2\) is the environmental
variance and \(u_{ei}\) are normal random variables with zero mean and
unit variance that are independent through time but may be correlated
between species. Demographic stochasticity arises from variations in
births and deaths among individuals (e.g., same states, different
fates), and is included in the model as a first-order, normal
approximation (Lande et al. 2003, {{de Mazancourt}} et al. 2013).
\(\sigma_{di}^2\) is the demographic variance and \(u_{di}(t)\) are
independent normal variables with zero mean and unit variance. To derive
analytical predictions we solved a first-order approximation of Equation
2 ({{de Mazancourt}} et al. 2013 and Online Supporting Information).
\textcolor{blue}{Due to the linear approximation approach, our analytical predictions will likely fail in communities where species exhibit large fluctuations due to limit cycles and chaos}
(Loreau and {{de Mazancourt}} 2008).
\textcolor{blue}{Indeed, one of the advantages of focusing on growth rates rather than abundances is that growth rates are more likely to be well-regulated around an equilibrium value, if the long-term average of a species' growth rate is relatively small}
(e.g., \(r < 2\)).

@@

Our first prediction assumes no interspecific interactions, no
environmental stochasticity, identical intrinsic growth rates, and that
demographic stochasticity is operating but all species have identical
demographic variances. This limiting case, \(\mathcal{M}_{D}\),
represents a community where dynamics are driven by demographic
stochasticity alone. Our prediction
\textcolor{blue}{for the synchrony of per capita growth rates for $\mathcal{M}_{D}$, $\phi_{R,\mathcal{M}_{D}}$, is}

@@

Our second limiting case assumes only environmental stochasticity is
operating (\(\mathcal{M}_{E}\)). Thus, we assume there are no
interspecific interactions, demographic stochasticity is absent,
intrinsic growth rates are identical, and environmental variance is
identical for all species. Our prediction
\textcolor{blue}{for the synchrony of per capita growth rates for $\mathcal{M}_{E}$, $\phi_{R,\mathcal{M}_{E}}$, is }

@@

\noindent{} where \(\text{cov}(u_{ei},u_{ej})\) is the standardized
covariance of environmental responses between species \emph{i} and
species \emph{j}. Confronting our theoretical predictions with data
requires estimates of species dynamics of large populations (no
demographic stochasticity) \textcolor{blue}{growing in isolation} (no
interspecific interactions) to calculate the covariance of species'
environmental responses. To estimate environmental responses in natural
communities, we turn to our population models built using long-term
demographic data.

@@

Vital rate regressions are the building blocks of our dynamic models: an
integral projection model (IPM) and an individual-based model (IBM). We
followed the approach of Chu and Adler (2015) to fit statistical models
for survival, growth, and recruitment (see Online Supporting Information
for full details). We modeled survival probability of each genet as
function of genet size, temporal variation among years, permanent
spatial variation among groups of quadrats, and local neighborhood
crowding from conspecific and heterospecific genets. Regression
coefficients for the effect of crowding by each species can be
considered a matrix of interaction coefficients whose diagonals
represent intraspecific interactions and whose off-diagonals represent
interspecific interactions (Adler et al. 2010). These interaction
coefficients can take positive (facilitative) or negative (competitive)
values. We modeled growth as the change in size of a genet from one year
to the next, which depends on the same factors as the survival model. We
fit the survival and growth regressions using INLA (Rue et al. 2014), a
statistical package for fitting generalized linear mixed effects models
via approximate Bayesian inference (Rue et al. 2009), in R (R Core Team
2013).
\textcolor{blue}{Crowding was treated as a fixed effect without a temporal component because most 95\% credible intervals for random year effects on crowding broadly overlapped zero and, in a test case, including yearly crowding effects did not change our results.}
Spatial (quadrat groupings) variation was treated as a random effect on
the intercept and temporal (interannual) variation was treated as random
effects on the intercept and the effect of genet size in the previous
year (Online Supporting Information).

@@

We performed simulation experiments where drivers (environmental
stochasticity, demographic stochasticity, or interspecific
\textcolor{blue}{interactions}) were removed one-by-one and in
combination. To remove interspecific interactions, we set the
off-diagonals of the interaction matrix for each vital rate regression
to zero. This retains intraspecific interactions, and thus
density-dependence, and results in simulations where species are
\textcolor{blue}{growing in isolation}.
\textcolor{blue}{We cannot definitively rule out the effects of species interactions on all parameters, meaning that a true monoculture could behave differently than our simulations of a population growing without interspecific competitors.}
To remove the effect of a fluctuating environment, we removed the
temporal (interannual) random effects from the regression equations. To
remove the effect of demographic stochasticity, we use the IPM rather
than the IBM because the IPM does not include demographic stochasticity
(demographic stochasticity cannot be removed from the IBM). Since the
effect of demographic stochasticity on population dynamics depends on
population size (Lande et al. 2003), we can control the strength of
demographic stochasticity by simulating the IBM on areas (e.g.~plots) of
different size. Indeed, results from an IBM with infinite population
size would converge on results from the IPM. Given computational
constraints, the largest landscape we simulate is a 25 \(\text{m}^2\)
plot.

We conducted the following six simulation experiments: (1) IBM: All
drivers (environmental stochasticity, demographic stochasticity, or
\textcolor{blue}{interspecific interactions}) present; (2) IPM:
Demographic stochasticity removed; (3) IBM: Environmental stochasticity
removed; (4) IBM: \textcolor{blue}{Interspecific interactions} removed;
(5) IPM: \textcolor{blue}{Interspecific interactions} and demographic
stochasticity removed; (6) IBM:
\textcolor{blue}{Interspecific interactions} and environmental
stochasticity removed. We ran IPM simulations for 2,000 time steps,
after an initial 500 iteration burn-in period. This allowed species time
to reach their stable size distribution. We then calculated the
synchrony of species' per capita growth rates over 100 randomly selected
contiguous 50 time-step sections. We ran IBM simulations for 100 time
steps, and repeated the simulations 100 times for each simulation
experiment. From those, we retained only the simulations in which no
species went extinct due to demographic stochasticity. Synchrony was
calculated over the 100 time steps for each no extinction run within a
model experiment. To explore the effect of demographic stochasticity in
different sized populations, we ran simulations (1) and (6) on plot
sizes of 1, 4, 9, 16, and 25 \(\text{m}^2\). All other IBM simulations
were run on a 25 \(\text{m}^2\) landscape.

Results from our simulation experiments also allow us to test our
theoretical predictions. First, in the absence of
\textcolor{blue}{interspecific interactions} and demographic
stochasticity,
\textcolor{blue}{populations can only fluctuate in response to the environment}.
Therefore, we can use results from simulation (5) to estimate the
covariance of species' responses to the environment
(\(\text{cov}(u_{ie}, u_{je})\)) and parameterize Equation 4.
Parameterizing Equation 3 does not require simulation output because the
only parameters are the species' relative abundances. Second,
simulations (5) and (6) represent the simulated version of our limiting
case theoretical predictions. Thus, we directly test the theoretical
predictions by comparing them to observed synchrony and simulated
synchrony.

@@

Synchrony of species' per capita growth rates at our study sites range
from 0.36 to 0.89 and synchrony of percent cover ranged from 0.15 to
0.92 (Table 2). Synchrony tends to be higher in communities with few
species (Arizona and New Mexico) and/or with relatively high temporal
variability in percent cover (e.g., Montana). Synchrony is lowest in
Idaho, the only data set that includes two life forms: a shrub and three
perennial grasses (Table 1).
\textcolor{blue}{Synchrony of per capita growth rates and CV of percent cover are positively correlated}
(Pearson's \(\rho\) = 0.72). For all five communities, species synchrony
from IPM and IBM simulations closely approximated observed synchrony
(Fig. S1). IBM-simulated synchrony is consistently, but only slightly,
lower than IPM-simulated synchrony (Fig. S1), likely due to the
desynchronizing effect of demographic stochasticity.

@@

Our theoretical predictions were derived from a simple model of
population dynamics and required several simplifying assumptions,
raising questions about their relevance to natural communities.
\textcolor{blue}{For example, the species in our communities do not have equivalent environmental and demographic variances (Figs. S4-S7), as required by our predictions.}
However, the theoretical predictions
\textcolor{blue}{closely matched results from} simulations of population
models fit to long-term data from natural plant communities (Table 3).
Such \textcolor{blue}{strong agreement} between our analytical
predictions and the simulation results should inspire confidence in the
ability of simple models to inform our understanding of species
synchrony
\textcolor{blue}{even in complex natural communities, and allows us to place our simulation results within the context of contemporary theory}.

>>>>

\documentclass[12pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={},
            colorlinks=true,
            citecolor=blue,
            urlcolor=black,
            linkcolor=black,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{0}

@@

\textbf{Running Head}: Drivers of species synchrony in natural plant communities

@@

\begin{abstract}
Temporal asynchrony among species helps diversity to stabilize ecosystem functioning, but identifying the mechanisms that determine synchrony remains a challenge.
Here, we refine and test theory showing that synchrony depends on three factors: species responses to environmental variation, interspecific interactions, and demographic stochasticity. We then conduct simulation experiments with empirical population models to quantify the relative importance of these factors in five plant communities.
We found that the average synchrony of per capita growth rates, which can range from 0 (perfect asynchrony) to 1 (perfect synchrony), was higher when environmental variation was present (0.62) rather than absent (0.43).
Removing interspecific interactions and demographic stochasticity had small effects on synchrony. In these plant communities, where species interactions and demographic stochasticity have little influence, synchrony reflects the covariance in species responses to the environment.

\emph{Key words: synchrony, compensatory dynamics, environmental stochasticity, demographic stochasticity, interspecific competition, stability}

\end{abstract}

\setlength{\parindent}{5ex}

@@

Ecosystems are being transformed by species extinctions (Cardinale et
al. 2012), changes in community composition (Vellend et al. 2013,
Dornelas et al. 2014), and anthropogenic environmental change (Vitousek
et al. 1997), impacting the provisioning and stability of ecosystem
services (Loreau et al. 2001, Hooper et al. 2005, Rockstrom et al.
2009). Experiments have provided compelling evidence that decreases in
species richness will decrease productivity (Tilman et al. 2001) and the
temporal stability of productivity (Tilman et al. 2006, Hector et al.
2010). The stabilizing effect of species richness stems from individual
species responding in different way\} to environmental fluctuations
(environmental stochasticity), or fluctuating asynchronously because of
random chance events (demographic stochasticity) (Isbell et al. 2009,
Hector et al. 2010, {{de Mazancourt}} et al. 2013). Species richness
affects synchrony because larger species pools are more likely to
contain species that respond disimilarly to environmental conditions
(Yachi and Loreau 1999), implying that species losses will reduce
ecosystem stability. Even without species losses, abiotic homogenization
can weaken compensatory dynamics and, in turn, decrease temporal
stability of ecosystem functioning (Hautier et al. 2014). The link
between synchrony and stability means that a mechanistic understanding
of synchrony can help us predict the impacts of global change on
ecosystem stability.

Theory identifies three main determinants of species synchrony:
environmental stochasticity, demographic stochasticity, and
interspecific interactions (Loreau and {{de Mazancourt}} 2008, 2013,
Gonzalez and Loreau 2009). For example, in a community composed of large
populations (no demographic stochasticity) with weak interspecific
interations, community-wide species synchrony should be determined by
the covariance of species' responses to the environment (Loreau and {{de
Mazancourt}} 2008). However, this prediction relies on a relatively
simple population model and only holds under two assumptions: (i)
species' responses to the environment are similar in magnitude and (ii)
all species have similar growth rates. Whether such theoretical
predictions hold in natural communities where species differences are
unlikely to be symmetrical is unkown because few studies have explicitly
tested theory on the drivers of species synchrony in natural communities
(Mutshinda et al. 2009, Thibaut et al. 2012), and they did not consider
demographic stochasiticity.

In grasslands, most empirical studies have focused on whether species
synchrony is primarily an outcome of species-specific responses to
environmental conditions (Hautier et al. 2014) or competition (Gross et
al. 2014). Even beyond grassland studies, whether competition or
environmental responses drive compensatory dynamics remains
controversial (reviewed in Gonzalez and Loreau 2009). In part,
controversy remains because quantifying the relative strengths of each
driver on the degree of synchrony from the covariance matrix of species
abundances (e.g., Houlahan et al. 2007) is impossible. This is because
an unbiased null expectation for synchrony does not exist (Loreau and
{{de Mazancourt}} 2008) and observed synchrony can arise from non-unique
combinations of factors (Ranta et al. 2008). For example, weak synchrony
of population abundances could reflect positive environmental
correlations (synchronizing effect) offset by strong competition
(desynchronizing effect), or negative environmental correlations and
weak competition.

The best way to quantify the effects of environmental stochasticity,
demographic stochasticity, and interspecific interactions is to remove
them one-by-one, and in combination. In principle, this could be done in
an extremely controlled laboratory setting, but empirically-based models
of interacting populations, fit with data sets from natural communities,
offer a practical alternative. For example, Mutshinda et al. (2009) fit
a dynamic population model to several community time series of insect
and bird abundances. They used a statistical technique to decompose
temporal variation into competition and environmental components, and
found that positively correlated environmental responses among species
determined community dynamics. Thibaut et al. (2012) used a similar
approach for reef fish and came to a similar conclusion: environmental
responses determine synchrony. While a major step forward, Mutshinda et
al.'s (2009) and Thibaut et al.'s (2012) modeling technique relied on
abundance data that may or may not reliably capture competitive
interactions that occur at the individual level. Furthermore, although
both studies quantified the relative importance of environmental
stochasticity and interspecific interactions to explain the observed
variation of species synchrony, they did not use the model to quantify
how much synchrony would change when each factor is removed.

Here, we use multi-species population models fit to long-term
demographic data from five semi-arid plant communities to test theory on
the drivers of species synchrony. Our objectives are to (1) derive and
test theoretical predictions of species synchrony and (2) determine the
relative influence of environmental stochasticity, demographic
stochasticity, and interspecific interactions on species synchrony in
natural plant communities. To achieve these objectives, we first refine
theory that has been used to predict the effects of species richness on
ecosystem stability ({{de Mazancourt}} et al. 2013) and species
synchrony (Loreau and {{de Mazancourt}} 2008) to generate predictions of
community-wide species synchrony under two limiting cases derived from
the dynamics of individual species in monoculture. We then confront our
theoretical predictions with simulations from the empirically-based
population models. Second, we use the multi-species population models to
perform simulation experiments that isolate the effects of environmental
stochasticity, demographic stochasticity, and interspecific interactions
on community-wide species synchrony. Given that our population models
capture the essential features of community dynamics important to
synchrony (density-dependence, and demographic and environmental
stochasticity), and that these models successfully reproduce observed
community dynamics (Chu and Adler 2015), perturbing the models can
reveal the processes that determine species synchrony in our focal
grassland communities.

@@

While existing theory has identified the factors driving synchrony, we
do not have a simple expression to predict synchrony in a particular
community with all factors operating simultaneously. However, we can
derive analytical predictions for species synchrony under special
limiting cases. The limiting case predictions we derive serve as
baselines to help us interpret results from empirically-based
simulations (described below). We focus on synchrony of per capita
growth rates, rather than abundances, because growth rates represent the
instantaneous response of species to the environment and competition,
and are less susceptible to the legacy effects of drift and disturbance
(Loreau and {{de Mazancourt}} 2008). We present equivalent results for
synchrony of species abundances in the Online Supporting Information,
and show that they lead to the same overall conclusions as synchrony of
per capita growth rates. Following Loreau and {{de Mazancourt}} (2008)
and {{de Mazancourt}} et al. (2013), we define population growth,
ignoring observation error, as

@@

\noindent where \(N_i(t)\) is the biomass of species \emph{i} in year
\emph{t}, and \(r_i(t)\) is its population growth rate in year \emph{t}.
\(r_{mi}\) is species \emph{i}`s intrinsic rate of increase, \(K_i\) is
its carrying capacity, and \(\alpha_{ij}\) is the interspecific
competition coefficient representing the effect of species \emph{j} on
species \emph{i}. Environmental stochasticity is incorporated as
\(\sigma_{ei}u_{ei}(t)\), where \(\sigma_{ei}^2\) is the environmental
variance and \(u_{ei}\) are normal random variables with zero mean and
unit variance that are independent through time but may be correlated
between species. Demographic stochasticity arises from variations in
births and deaths among individuals (e.g., same states, different
fates), and is included in the model as a first-order, normal
approximation (Lande et al. 2003, {{de Mazancourt}} et al. 2013).
\(\sigma_{di}^2\) is the demographic variance and \(u_{di}(t)\) are
independent normal variables with zero mean and unit variance. To derive
analytical predictions we solved a first-order approximation of Equation
2 ({{de Mazancourt}} et al. 2013 and Online Supporting Information). Due
to the linear approximation approach, our analytical predictions will
likely fail in communities where species exhibit large fluctuations due
to limit cycles and chaos (Loreau and {{de Mazancourt}} 2008). Indeed,
one of the advantages of focusing on growth rates rather than abundances
is that growth rates are more likely to be well-regulated around an
equilibrium value, if the long-term average of a species' growth rate is
relatively small (e.g., \(r < 2\)).

@@

Our first prediction assumes no interspecific interactions, no
environmental stochasticity, identical intrinsic growth rates, and that
demographic stochasticity is operating but all species have identical
demographic variances. This limiting case, \(\mathcal{M}_{D}\),
represents a community where dynamics are driven by demographic
stochasticity alone. Our prediction for the synchrony of per capita
growth rates for \(\mathcal{M}_{D}\), \(\phi_{R,\mathcal{M}_{D}}\), is

@@

Our second limiting case assumes only environmental stochasticity is
operating (\(\mathcal{M}_{E}\)). Thus, we assume there are no
interspecific interactions, demographic stochasticity is absent,
intrinsic growth rates are identical, and environmental variance is
identical for all species. Our prediction for the synchrony of per
capita growth rates for \(\mathcal{M}_{E}\),
\(\phi_{R,\mathcal{M}_{E}}\), is

@@

\noindent{} where \(\text{cov}(u_{ei},u_{ej})\) is the standardized
covariance of environmental responses between species \emph{i} and
species \emph{j}. Confronting our theoretical predictions with data
requires estimates of species dynamics of large populations (no
demographic stochasticity) growing in isolation (no interspecific
interactions) to calculate the covariance of species' environmental
responses. To estimate environmental responses in natural communities,
we turn to our population models built using long-term demographic data.

@@

Vital rate regressions are the building blocks of our dynamic models: an
integral projection model (IPM) and an individual-based model (IBM). We
followed the approach of Chu and Adler (2015) to fit statistical models
for survival, growth, and recruitment (see Online Supporting Information
for full details). We modeled survival probability of each genet as
function of genet size, temporal variation among years, permanent
spatial variation among groups of quadrats, and local neighborhood
crowding from conspecific and heterospecific genets. Regression
coefficients for the effect of crowding by each species can be
considered a matrix of interaction coefficients whose diagonals
represent intraspecific interactions and whose off-diagonals represent
interspecific interactions (Adler et al. 2010). These interaction
coefficients can take positive (facilitative) or negative (competitive)
values. We modeled growth as the change in size of a genet from one year
to the next, which depends on the same factors as the survival model. We
fit the survival and growth regressions using INLA (Rue et al. 2014), a
statistical package for fitting generalized linear mixed effects models
via approximate Bayesian inference (Rue et al. 2009), in R (R Core Team
2013). Crowding was treated as a fixed effect without a temporal
component because most 95\% credible intervals for random year effects
on crowding broadly overlapped zero and, in a test case, including
yearly crowding effects did not change our results. Spatial (quadrat
groupings) variation was treated as a random effect on the intercept and
temporal (interannual) variation was treated as random effects on the
intercept and the effect of genet size in the previous year (Online
Supporting Information).

@@

We performed simulation experiments where drivers (environmental
stochasticity, demographic stochasticity, or interspecific interactions)
were removed one-by-one and in combination. To remove interspecific
interactions, we set the off-diagonals of the interaction matrix for
each vital rate regression to zero. This retains intraspecific
interactions, and thus density-dependence, and results in simulations
where species are growing in isolation. We cannot definitively rule out
the effects of species interactions on all parameters, meaning that a
true monoculture could behave differently than our simulations of a
population growing without interspecific competitors. To remove the
effect of a fluctuating environment, we removed the temporal
(interannual) random effects from the regression equations. To remove
the effect of demographic stochasticity, we use the IPM rather than the
IBM because the IPM does not include demographic stochasticity
(demographic stochasticity cannot be removed from the IBM). Since the
effect of demographic stochasticity on population dynamics depends on
population size (Lande et al. 2003), we can control the strength of
demographic stochasticity by simulating the IBM on areas (e.g.~plots) of
different size. Indeed, results from an IBM with infinite population
size would converge on results from the IPM. Given computational
constraints, the largest landscape we simulate is a 25 \(\text{m}^2\)
plot.

We conducted the following six simulation experiments: (1) IBM: All
drivers (environmental stochasticity, demographic stochasticity, or
interspecific interactions) present; (2) IPM: Demographic stochasticity
removed; (3) IBM: Environmental stochasticity removed; (4) IBM:
Interspecific interactions removed; (5) IPM: Interspecific interactions
and demographic stochasticity removed; (6) IBM: Interspecific
interactions and environmental stochasticity removed. We ran IPM
simulations for 2,000 time steps, after an initial 500 iteration burn-in
period. This allowed species time to reach their stable size
distribution. We then calculated the synchrony of species' per capita
growth rates over 100 randomly selected contiguous 50 time-step
sections. We ran IBM simulations for 100 time steps, and repeated the
simulations 100 times for each simulation experiment. From those, we
retained only the simulations in which no species went extinct due to
demographic stochasticity. Synchrony was calculated over the 100 time
steps for each no extinction run within a model experiment. To explore
the effect of demographic stochasticity in different sized populations,
we ran simulations (1) and (6) on plot sizes of 1, 4, 9, 16, and 25
\(\text{m}^2\). All other IBM simulations were run on a 25
\(\text{m}^2\) landscape.

Results from our simulation experiments also allow us to test our
theoretical predictions. First, in the absence of interspecific
interactions and demographic stochasticity, populations can only
fluctuate in response to the environment. Therefore, we can use results
from simulation (5) to estimate the covariance of species' responses to
the environment (\(\text{cov}(u_{ie}, u_{je})\)) and parameterize
Equation 4. Parameterizing Equation 3 does not require simulation output
because the only parameters are the species' relative abundances.
Second, simulations (5) and (6) represent the simulated version of our
limiting case theoretical predictions. Thus, we directly test the
theoretical predictions by comparing them to observed synchrony and
simulated synchrony.

@@

Synchrony of species' per capita growth rates at our study sites range
from 0.36 to 0.89 and synchrony of percent cover ranged from 0.15 to
0.92 (Table 2). Synchrony tends to be higher in communities with few
species (Arizona and New Mexico) and/or with relatively high temporal
variability in percent cover (e.g., Montana). Synchrony is lowest in
Idaho, the only data set that includes two life forms: a shrub and three
perennial grasses (Table 1). Synchrony of per capita growth rates and CV
of percent cover are positively correlated (Pearson's \(\rho\) = 0.72).
For all five communities, species synchrony from IPM and IBM simulations
closely approximated observed synchrony (Fig. S1). IBM-simulated
synchrony is consistently, but only slightly, lower than IPM-simulated
synchrony (Fig. S1), likely due to the desynchronizing effect of
demographic stochasticity.

@@

Our theoretical predictions were derived from a simple model of
population dynamics and required several simplifying assumptions,
raising questions about their relevance to natural communities. For
example, the species in our communities do not have equivalent
environmental and demographic variances (Figs. S4-S7), as required by
our predictions. However, the theoretical predictions closely matched
results from simulations of population models fit to long-term data from
natural plant communities (Table 3). Such strong agreement between our
analytical predictions and the simulation results should inspire
confidence in the ability of simple models to inform our understanding
of species synchrony even in complex natural communities, and allows us
to place our simulation results within the context of contemporary
theory.
